### 2019-03-14 chapters/6_conclusions.tex
Move to the main repository folder

% !TEX root = ../agglo_clust_review.tex
\subsection{Results on Cityscapes}

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{c| c| c | c}
        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
\textbf{mean} & False & {\color{ForestGreen} 0.3429 } & {\color{ForestGreen} 0.5516 } \\
% MEAN finetuned affs avg thresh035 use log costs & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
mean & True & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
% MEAN constr finetuned affs avg thresh035 use log costs & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
sum & False & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
% GAEC finetuned affs avg thresh035 dont use log costs & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Results on cityscapes validation set (with finetuned affinities)}
    \label{tab:linkage-criteria}
\end{table*}

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{c| c| c | c}
        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
mean & False & {\color{Orange} 0.3359 } & {\color{ForestGreen} 0.5416 } \\
mean & True & {\color{Orange} 0.3315 } & {\color{ForestGreen} 0.5331 } \\
MutexWatershed & True & {\color{Red} 0.2123 } & {\color{Red} 0.3848 } \\
SingleLinkage & False & {\color{Red} 0.1935 } & {\color{Red} 0.3615 } \\
CompleteLinkage & False & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Scores on cityscapes validation set (original affinities trained by GMIS)}
    \label{tab:linkage-criteria}
\end{table*}

% \begin{table*}
%     \centering
%     \begin{subtable}[t!]{0.98\textwidth}\centering
%         \begin{tabular}{c| c | c | c}
% Update rule & \makecell{Use Cannot-Link\\Constraints} & \makecell{Multicut objective} & Runtime (s)\\ \midrule\midrule
% sum & false & \textbf{-150873} & 99 (??) \\
% sum & true & -150873 & 249 \\
% MutexWatershed & false & -150854 & 100 \\
% mean & false & -150850 & 105 \\
% mean & true & -150848 & 244 \\
% max & true & -149441 & 459 \\
% min & true & -147663 & 186 \\
% min & false & -147663 & 82 \\
% max & false & -103614 & \textbf{16} \\
%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Compare update-rules on fruit-fly large graph}
%     \label{tab:linkage-criteria}
% \end{table*}

>>>>

% !TEX root = ../agglo_clust_review.tex
\section{Conclusions}
